Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-07 ms.tex
section clarifying parameters sampled during MCMC

Here $u_{\nu_i, IRAS}$ gives the conversion factor from $K_{CMB}$ to MJy/sr
for band $\nu_i$ under the `\IRAS~convention', which corresponds to
a power law specrum with spectral index $\alpha$=$-1$. The values of 
$u_{\nu_i, IRAS}$ are listed in the second column of \cite{planckresponse} 
Table 6. $u_{\nu_i, IRAS \ to \ (T, \beta)}$ is a color correction factor 
relative to the \IRAS~convention for band $\nu_i$, assuming a MBB($T$, $\beta$)
spectrum. In practice, we retrieve $u_{\nu_i}(T, \beta)$ in a fashion similar 
to that used for the $b_{\nu_i}(T, \beta)$ color corrections, using a set of 
precomputed one-dimensional look-up tables. To reiterate, for $\nu_i$$\le$353 
GHz $u_{\nu_i}(T_k, \beta_k)$ has units of (MJy/sr)/$K_{CMB}$, and therefore 
$\tilde{I}_{\nu_{i}}$ will have different units depending on the band $\nu_i$, 
though $\tilde{I}_{\nu_{i}}$ always has the same units as the native band 
$\nu_i$ map.

% add a sentence in the middle of the previous paragraph explaining why
% it doesn't make sense to just multiply the Kcmb maps by some factor
% and pretend they're in MJy/sr for the sake of making predictions

%The \PLANCK~100-353 GHz data are provided in units of $K_{CMB}$, while 
%\verb|i100| and the higher frequency HFI maps are provided in units of 
%MJy/sr.

We will treat the SED normalization $\tilde{I}_{545}$ as a free 
parameter in our fitting procedure. In our baseline fits, second free parameter
 is $T_2$, which determines the shape of the SED through $M_{\nu}$ as well as 
$b_{\nu_i}(T_2)$.

% (here SFD \verb|i100|) and that of \cite{planckdust}).

@@

\subsection{Markov Chains}
\label{sec:mcmc}
As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
per-pixel dust emission SED are the hot dust temperature $T_2$, which 
determines the shape of the SED, and the spectrum normalization. In practice,
the normalization is controlled via $\tilde{I}_{545}$, the amplitude of the 
model SED in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a 
Metropolis-Hastings Markov chain sampling the posterior probability as a 
function of the two parameters $T_2$ and $\tilde{I}_{545}$. For each pixel, we 
are sampling the posterior given by:

>>>>

Here $u_{\nu_i, IRAS}$ gives the conversion factor from $K_{CMB}$ to MJy/sr
for band $\nu_i$ under the `\IRAS~convention', which corresponds to
a power law specrum with spectral index $\alpha$=$-1$. The values of 
$u_{\nu_i, IRAS}$ are listed in the second column of \cite{planckresponse} 
Table 6. $u_{\nu_i, IRAS \ to \ (T, \beta)}$ is a color correction factor 
relative to the \IRAS~convention for band $\nu_i$, assuming a MBB($T$, $\beta$)
spectrum. In practice, we retrieve $u_{\nu_i}(T, \beta)$ values in a fashion 
similar to that used for the $b_{\nu_i}(T, \beta)$ color corrections, using a 
set of precomputed one-dimensional look-up tables. To reiterate, for 
$\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ has units of (MJy/sr)/$K_{CMB}$,
and therefore $\tilde{I}_{\nu_{i}}$ will have different units depending on the 
band $\nu_i$, though $\tilde{I}_{\nu_{i}}$ always has the same units as the 
native band $\nu_i$ map.

%We will treat the SED normalization $\tilde{I}_{545}$ as a free 
%parameter in our fitting procedure. In our baseline fits, second free 
%parameter is $T_2$, which determines the shape of the SED through $M_{\nu}$ as
% well as $b_{\nu_i}(T_2)$.

@@

\subsection{Sampling Parameters}
As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
 fixed, while the dust spectrum normalization and dust temperature vary for
each line-of-sight. In order to predict the dust SED for a given pixel, we are 
therefore left with two remaining degrees of freedom, and must choose an 
appropriate set of two parameters to sample and thereby constrain via MCMC. To 
determine the SED normalization in each pixel, we draw samples in 
$\tilde{I}_{545}$, the broadband intensity in the 545 GHz bandpass, as defined 
in Equation \ref{eqn:inten}. With the four aforementioned global parameters 
fixed, the dust spectrum shape is determined entirely by the two dust 
temperatures, which are coupled. To constrain the dust temperatures,
 we sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we 
compute the corresponding value of $T_1$, thereby specifying ($\beta$, $T$) for
both MBB components and thus fully specifying the SED shape.

For the lower resolution fits described in $\S$\ref{sec:lores}, we sample
in three parameters: $\tilde{I}_{545}$, $T_2$, and $f_1$.

% sentence or two mentioning reduced resolution fits where we sample in
% three dimensions (f_1, T_2, tilde{I}_{545})

\subsection{Markov Chains}
\label{sec:mcmc}

As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
per-pixel dust emission SED are the hot dust temperature $T_2$, which 
determines the shape of the SED, and the spectrum normalization. In practice,
the normalization is controlled via $\tilde{I}_{545}$, the amplitude of the 
model SED in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a 
Metropolis-Hastings Markov chain sampling the posterior probability as a 
function of the two parameters $\tilde{I}_{545}$ and $T_2$. For each pixel, we 
are sampling the posterior given by:
